---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: console
---
When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

# <font color='#31708f'>Zendesk Tickets Word Cloud</font>

* [Preprocessing](#second-bullet)

* [WordCloud](#third-bullet)

* [CountVectorizer](#fourth-bullet)

* [LDA Model](#fifth-bullet)

List all environments:
```{r}
ls()
```
Create new environment named 'test':
```{r}
test <- new.env() 
```

Check if the new environment got created:
```{r}
ls()
```
Register the new environment:
```{r}
attach(test)
```

```{r}
install.packages("renv")
```

Set your working directory to the project folder.
```{r}
setwd("/home/smsta/Desktop/r_zendesk_tag_cloud")
```

```{r}
library(renv)
```

```{r}
renv::init()
```

```{r}
status_info <- renv::status()
installed_packages <- status_info$packages$status == "installed"
print(status_info$packages$package[installed_packages])
```











